On Secure Delegation of SampBQP with a Classical Client

### 2019-12-23 qpip.tex
Change protocol section heading
Start last subsection

\section{Our QPIP Scheme}

@@

\Ethan{TODO read Mahadev's?}

>>>>

\section{Our Delegation Protocols}

@@

Here we combine the above scheme with results from \cite{mahadev_delegation} to create a delegation protocol for $\SampBQP$ for fully classical clients.

We first describe the construction in \cite{mahadev_delegation}.

\begin{theorem}
	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol that...
	\begin{itemize}
		\item x
		\item y
		\item z
	\end{itemize}
\end{theorem}
\begin{proof}
	Construction given in \cite{mahadev_delegation}
\end{proof}

\Ethan{TODO}
